Multi-Domain Adaptation in Neural Machine Translation with Dynamic Sampling Strategies

### 2022-05-16 2022/eamt/eamt-latex/eamt22.tex
fixed length and ref issue

\documentclass[11pt]{article}
\usepackage{eamt22}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage[small,bf]{caption} % added MLF 20171211
\setlength\titlebox{6.5cm}    % Expanding the titlebox
%%% YOUR PACKAGES BELOW THIS LINE %%%

@@

\author{Minh-Quang Pham\\
  Uni. Paris-Saclay,  CNRS, LISN \\
  F-91405 Orsay \\
  {\tt pham@limsi.fr}  \And
  \textbf{Josep Crego}\\
  SYSTRAN ,\\
  5 rue Feydeau, F-75002 Paris\\
  {\tt crego@systrangroup.com} \And
  Fran\c cois Yvon\\
  Uni. Paris-Saclay, CNRS, LISN\\
  F-91405 Orsay, France\\
  {\tt yvon@limsi.fr}}

@@

%\usepackage[noend]{algpseudocode}
\usepackage{regexpatch}
\usepackage{subcaption}
% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

\usepackage{url}
\usepackage{longtable}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage[draft]{todo}
\usepackage[normalem]{ulem}
\usepackage{xspace}
\usepackage{float}

@@

\let\oldbibitem\bibitem
\def\bibitem{\vfill\oldbibitem}

\usepackage{soulutf8}
\usepackage{tabularx}

\usepackage{multirow}
\usepackage{adjustbox}
\usepackage{caption}
\usepackage{subcaption}

@@

\newcommand{\vlambda}{\ensuremath{\boldsymbol\lambda}\xspace} % parameters vector for a distribution
\newcommand{\vtheta}{\ensuremath{\boldsymbol\theta}\xspace} % parameters vector for a distribution
\newcommand{\vpsi}{\ensuremath{\boldsymbol\psi}\xspace} % parameters vector for a distribution
\newcommand{\indic}[1]{\ensuremath{\mathbb{I}(#1)}}
% \newcommand{\SB}[1]{\textcolor{green}{#1}}
% \newcommand{\SW}[1]{\textcolor{red}{#1}}
\newcommand{\SB}[1]{\textbf{#1}}
\newcommand{\SW}[1]{\underline{#1}}
% limits underneath
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\renewcommand\textfraction{.1}
\renewcommand\floatpagefraction{.95}
\newcommand{\sbcl}[2]{{\scriptsize #1 \hfill $|$ \hfill  #2}}
\usepackage{multirow}
\usepackage{adjustbox}
\usepackage[hidelinks]{hyperref}
\makeatletter
\newenvironment{breakablealgorithm}
  {% \begin{breakablealgorithm}
   \begin{center}
     \refstepcounter{algorithm}% New algorithm
     \hrule height.8pt depth0pt \kern2pt% \@fs@pre for \@fs@ruled
     \renewcommand{\caption}[2][\relax]{% Make a new \caption
       {\raggedright\textbf{\fname@algorithm~\thealgorithm} ##2\par}%
       \ifx\relax##1\relax % #1 is \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##2}%
       \else % #1 is not \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##1}%
       \fi
       \kern2pt\hrule\kern2pt
     }
  }{% \end{breakablealgorithm}
     \kern2pt\hrule\relax% \@fs@post for \@fs@ruled
   \end{center}
  }
\makeatother

@@

These situations have been amply documented from a theoretical perspective (eg.\ \cite{Mansour09multiple,Mansour09domainadaptation,Hoffman18algorithms}). A general recommendation in the DA setting is to adjust the sampling distribution used to optimize the system so as to compensate for the mismatch between $\mathcal{D}^s(x)$ and $\mathcal{D}^t(x)$. This can be approximated by reweighting instances, or more conveniently domains, which are selected during training with a probability $\lambda^{l}(d)$, with $\lambda^{l}(d) \neq \lambda^{s}(d)$.

@@

Multidomain NMT (MDMT) aims to develop systems that simultaneously bode well for several domains. Like for DA, techniques for supervised MDMT combine one or several ingredients: (a) the specialization of data representations \cite{Kobus17domaincontrol} or of sub-networks \cite{Pham19generic} to differentiate the processing of each domain; (b) the use of adversarial techniques to neutralize differences between domains \cite{Britz17mixing,Zeng18multidomain}; (c) the use of automatic domain identification e.g.\ \cite{Jiang19multidomain}. Unsupervised MDMT is studied in \newcite{Farajian17multidomain}, as an instance of unsupervised DA.

@@

\bibliography{multidomain}
\bibliographystyle{eamt22}
% \clearpage{}

>>>>

\documentclass[11pt]{article}
\usepackage{eamt22}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage[small,bf]{caption} % added MLF 20171211
\setlength\titlebox{6.8cm}    % Expanding the titlebox
%%% YOUR PACKAGES BELOW THIS LINE %%%

@@

\author{Minh-Quang Pham\\
  Uni. Paris-Saclay,  CNRS, LISN \\
  F-91405 Orsay \\
  {\tt pham@limsi.fr}  \And
  Josep Crego\\
  SYSTRAN ,\\
  5 rue Feydeau, F-75002 Paris\\
  {\tt crego@systrangroup.com} \And
  Fran\c cois Yvon\\
  Uni. Paris-Saclay, CNRS, LISN\\
  F-91405 Orsay, France\\
  {\tt yvon@limsi.fr}}

@@

%\usepackage[noend]{algpseudocode}
% \usepackage{regexpatch}
% \usepackage{subcaption}
% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

\usepackage{longtable}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage[draft]{todo}
\usepackage[normalem]{ulem}
\usepackage{xspace}
\usepackage{float}

@@

%\let\oldbibitem\bibitem
% \def\bibitem{\vfill\oldbibitem}

\usepackage{soulutf8}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{subcaption}
% \usepackage{hyperref}

@@

\newcommand{\vlambda}{\ensuremath{\boldsymbol\lambda}\xspace} % parameters vector for a distribution
\newcommand{\vtheta}{\ensuremath{\boldsymbol\theta}\xspace} % parameters vector for a distribution
\newcommand{\vpsi}{\ensuremath{\boldsymbol\psi}\xspace} % parameters vector for a distribution
\newcommand{\indic}[1]{\ensuremath{\mathbb{I}(#1)}}
% \newcommand{\SB}[1]{\textcolor{green}{#1}}
% \newcommand{\SW}[1]{\textcolor{red}{#1}}
\newcommand{\SB}[1]{\textbf{#1}}
\newcommand{\SW}[1]{\underline{#1}}
% limits underneath
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\renewcommand\textfraction{.1}
\renewcommand\floatpagefraction{.95}
\newcommand{\sbcl}[2]{{\scriptsize #1 \hfill $|$ \hfill  #2}}

\makeatletter
\newenvironment{breakablealgorithm}
  {% \begin{breakablealgorithm}
   \begin{center}
     \refstepcounter{algorithm}% New algorithm
     \hrule height.8pt depth0pt \kern2pt% \@fs@pre for \@fs@ruled
     \renewcommand{\caption}[2][\relax]{% Make a new \caption
       {\raggedright\textbf{\fname@algorithm~\thealgorithm} ##2\par}%
       \ifx\relax##1\relax % #1 is \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##2}%
       \else % #1 is not \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##1}%
       \fi
       \kern2pt\hrule\kern2pt
     }
  }{% \end{breakablealgorithm}
     \kern2pt\hrule\relax% \@fs@post for \@fs@ruled
   \end{center}
  }
\makeatother

@@

These situations have been amply documented from a theoretical perspective \cite{Mansour09multiple,Mansour09domainadaptation,Hoffman18algorithms}. A general recommendation in the DA setting is to adjust the sampling distribution used to optimize the system so as to compensate for the mismatch between $\mathcal{D}^s(x)$ and $\mathcal{D}^t(x)$. This can be approximated by reweighting instances, or more conveniently domains, which are selected during training with a probability $\lambda^{l}(d)$, with $\lambda^{l}(d) \neq \lambda^{s}(d)$.

@@

Multidomain NMT (MDMT) aims to develop systems that simultaneously bode well for several domains. Like for DA, techniques for supervised MDMT combine one or several ingredients: (a) the specialization of data representations \cite{Kobus17domaincontrol} or of sub-networks \cite{Pham19generic} to differentiate the processing of each domain; (b) the use of adversarial techniques to neutralize differences between domains \cite{Britz17mixing,Zeng18multidomain}; (c) the use of automatic domain identification e.g.\ \cite{Jiang19multidomain}. Unsupervised MDMT is studied in \cite{Farajian17multidomain}, as an instance of unsupervised DA.

@@

\bibliography{multidomain}
\bibliographystyle{eamt22}

% \clearpage{}
